\documentclass{ceurart}

\usepackage{acronym}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{enumitem}

\renewcommand{\acffont}[1]{\textsl{#1}}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2023}
\copyrightclause{Copyright for this paper by its authors.\\
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{CLEF 2023: Conference and Labs of the Evaluation Forum, September 18--21, 2023, Thessaloniki, Greece}

%%
%% The "title" command
\title{SEUPD@CLEF: Team JIHUMING on Enhancing Search Engine Performance with Character N-Grams, Query Expansion, and Named Entity Recognition}

\title[mode=sub]{Notebook for the LongEval Lab at CLEF 2023}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Isil Atabek}[%
email=isil.atabek@studenti.unipd.it
]

\author[1]{Huimin Chen}[%
email=huimin.chen@studenti.unipd.it
]

\author[1]{Jes\'us Moncada-Ram\'irez}[%
email=jesus.moncadaramirez@studenti.unipd.it
]

\author[1]{Nicol\`o Santini}[%
email=nicolo.santini.1@studenti.unipd.it
]

\author[1]{Giovanni Zago}[%
email=giovanni.zago.3@studenti.unipd.it
]

\author[1]{Nicola Ferro}[%
orcid=0000-0001-9219-6239,
email=ferro@dei.unipd.it,
url=http://www.dei.unipd.it/~ferro/,
]

\address[1]{University of Padua, Italy}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  % Presentation
  Our group will propose a novel search engine for the Longitudinal Evaluation of Model Performance (LongEval) task at
  CLEF 2023~\cite{LongEval};
  it will also be the final work of the subject Search Engines at the University of Padova.
  % Objective
  Our system focuses on the short-term and long-term temporal persistence of the systems' performance, for a collection
  of both English and French documents.
  % Approach
  Our approach involves considering both English and French versions of the documents using whitespace tokenization,
  stopword removal and stemming.
  We generate character N-grams to identify recurring word structures (as prefixes or suffixes) repeated over documents.
  We also use query expansion with synonyms (in English) and some Natural Language Processing (NLP) techniques as Named
  Entity Recognition (NER) to further refine our system.
  The similarity function utilized in our approach is BM25.
  Our system was developed in Java and primarily utilized the Lucene library.
  % Experiments
  After extensive experiments on these techniques, we came up with five systems that have produced the best results in
  terms of MAP and NDCG scores.
  We analyzed these five selected systems by examining their MAP, NDCG, and Rprec scores on the test data.
  Additionally, we performed a Two-Way ANOVA to assess the AP of these systems.
  To compare our systems with each other, we will utilize the Tukey Honestly Significant Difference (HSD) test.
  % Results
  In summary, our analysis indicates that incorporating French queries enhances search results, larger N-gram sizes
  contribute to improved effectiveness, while our NER approach negatively affects the scores.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  CLEF 2023 \sep
  Information retrieval \sep
  LongEval \sep
  English \sep
  French \sep
  Search Engines
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{section/introduction}

\input{section/related}

\input{section/methodology}

\input{section/architecture}

\input{section/setup}

%\input{section/runs_selection}

\input{section/results}

\input{section/conclusion}

%% Define the bibliography file to be used
\bibliography{bibliography,proceedings}

\input{acronyms}


\end{document}
